---
title: ""
output: github_document
---

```{r, setup, include=FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  echo = FALSE
)
```

## Purpose
The purpose of this Shiny application is to interactively and quickly review previously found genetic Inflammatory Bowel Disease associations identified by the Cedars-Sinai F. Widjaja Foundation Inflammatory Bowel and Immunobiology Research Institute.

## Functionality
### Search
Users can search associations by **Gene** (e.g. NOD2), **Position** (e.g. Chr. 16, between 50731050-50766987), **RS ID** (e.g. rs5743293), or by **File** of either a list of genes or SNPs. Searching by position queries by the position of the SNP not by the position of the Gene. 

Users can search by multiple Genes or SNPs at a time by selecting multiple Genes or SNPs respectively. If a user has a large list of Genes or SNPs they can copy and paste them into the search box but the Genes/SNPs must be in comma separated format (e.g. IL1,IL2,IL3,IL4,IL5,IL6,IL7,IL8,IL9,IL10,IL11).

If you are going to upload a list of Genes or SNPs, the file **must** consist of a single column of Genes or RS IDs in .csv format. The column can be named or un-named. 

### Filtering
Users can filter their query to only include SNP associations that reach user defined thresholds. Users can filter by:

1. P Value
2. Minor Allele Frequency
3. SNP Location (e.g. intron, coding, complex...)
4. Overall Missingness
5. Overall Hardy-Weinberg Assumptions

Once a table of results is returned, a user can sub-filter the table by the output to further narrow down the results. 

### Download Data
For users who are interested in downloading their query, a **Download** button can be found at the bottom of every table. The downloaded data will reflect the filters applied from the query, but the "sub-filters" will not be applied. 

## Data 

```{r echo = FALSE}
print("hello github")
```

### Guidance for Analysts Submitting Association Data
The backbone of the application is genetic association tests performed by scientists at the Cedars-Sinai Inflammatory Bowel and Immunobiology Research Institute. To have your association stored in this application the following information is needed in a CSV file per association performed.

1. Illumina Chip ID
2. P Value
3. Odds Ratio or B Value 
4. Confidence Intervals (if performed)
5. The number of patients in the association (total number in association, both cases and controls)
6. A1

In addition to the above the analyst will need to submit information on:

1. The name of the analyst who performed the association
2. The year the analysis was run
3. The sample of patients the association was performed on (e.g. Disease Sub-Type (CD or UC), Race, Ethnicity, Jewish, other unique criteria of your analysis)
4. The phenotype tested


### Annotations
Specific information provided by Talin will go here. Plan is to use hg19 genome locations and UCSC gene information.
Hardy-Weinberg, minor allele frequency, and missingness will be performed globally on all runs. Additional details to follow. 

## Created By
The Cedars-Sinai F. Widjaja Foundation Inflammatory Bowel and Immunobiology Research Institute Translational Genomics Group.




